--- 
title: "Grading report TEST"
subtitle:  "Author: `r paste0(params$firstname, ' ', params$name)`" 
author: "This report was built by AUTHOR" 
date: "`r Sys.Date()`"
numbersections: FALSE 
lang: de-De
geometry: margin=1.1in
urlcolor: blue
linkcolor: blue

params:
  name: "Test"
  firstname: "Testfirst"
  crit1: 1.00
  crit2: 1.99
  crit3: 2.023

output: 
  pdf_document:
    includes:
      in_header: latex-header.tex
---


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(
  fig.align = "center",
  echo = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
library(knitcitations)
```

\thispagestyle{fancy}

\vspace{2cm}


```{r echo = FALSE}
options(digits = 2)
```


# Subject of Assessment

This report provides feedback to  `r params$name`, `r params$firstname`. The assessment subject is *Quirkology*.

```{r echo = FALSE}
grade_range <- c(
  "1,0" = 1.0, "1,3" = 1.3,
  "1,7" = 1.7, "2,0" = 2, "2,3" = 2.3,
  "2,7" = 2.7, "3,0" = 3, "3,3" = 3.3,
  "3,7" = 3.7, "4,0" = 4, "4,3" = 4.3,
  "5,0" = 5.0
)

grade_total <- mean(c(params$crit1, params$crit2, params$crit3))

grade_pos <- which.min(abs(unlist(grade_total) - grade_range))

name_grade_total <- names(grade_range[grade_pos])
```



# Assessment criteria and grading of assessment criteria

Assessment criterion                             Grade
----------------------------------------------- ----------------------
1. Formale Korrektheit des Berichts:            `r sprintf("%1.2f", params$crit1)`
2. Fachliche Güte des Berichts:                 `r sprintf("%1.2f",params$crit2)`
3. Argumentationsgüte des Berichts:             `r sprintf("%1.2f",params$crit3)`
----------------------------------------------- ----------------------


# Total grade




Die Arbeit wird im Ergebnis beurteilt mit der **Grade `r name_grade_total`**. 

*Notice that* Die Gesamtnote muss sich nicht als arithmetisches Mittel der Teilnoten ergeben.


\vspace{20 mm}


Professor Dr. I Dunno, `r Sys.Date()`

\vspace{20 mm}


